\chapter{Initial Feasibility Analysis}
\begin{spacing}{1.0}
\setlength{\parskip}{0.2in}
\graphicspath{{./Chapter2/}}

\section{Introduction}
AKASH DTH has been providing direct to home service across the country. They brought this service first ever in Bangladesh with an aim to win the hearts of millions with its commitment to quality services that will revolutionize the entertainment industry in the country.
\newline
As AKASH DTH looks forward to take the nationwide tv viewing experience to next level and be the leader among the tv service provider in Bangladesh; so customer satisfaction should be very important thing. An user friendly system can deliver best customer satisfaction. User problems and needs should be identified and solved. Some of problems are identified here initially and we recommend some solutions. The company should take proper steps based on these suggestions.

\section{Initial Feasibility Study}
An initial feasibility study means the test of a system proposal according to its impact on the organization, work ability, ability to meet user needs and effective use of existing resources. The objective of the feasibility study is not to solve the problem. It creates a sense of its scope and resultant a formal proposal.
\subsection{Feasibility Study of the Problems}
\subparagraph{1. statement of the problem}
As the service is satellite based so bad weather occurs transmission problem. In time of rain or most cloudy weather dish co not catch the signal properly and users may not be able to watch the TV coverage properly.
\subparagraph{Summary of Findings}
company should provide good transponders installed and to check that there are no joints between connection cables.
\subparagraph{Details of Findings}
There can be many reasons for signal problem. Besides bad weather, there could be many reasons for bad reception and some include wire disturbances, wrong choice of transponder etc. These bad signal issues hamper picture quality and consumers deprive of good watching experience from their television. So, this problem should take seriously.
\subparagraph{Recommendations and Conclusions}
When the installation process is being carried out, they have to make sure that the transponders get maximum signals. During installation, the signal strength of each of these transponders must be checked properly.

\subparagraph{2. statement of the problem}
In context of Bangladeshi user pricing is very important factor. The monthly charge seems overpriced to the consumer.
\subparagraph{Summary of Findings}
the company should look even better on the pricing to attract more consumer and satisfy their present customer.
\subparagraph{Details of Findings}
Most of the Bangladeshi consumers are price sensitive in any field. The regular cable connections are less costly. DTH service installation cost and monthly cost are overpriced to customers. Which we get from our initial finding.
\subparagraph{Recommendations and Conclusions}
So, company should reduce their price promoting attractive packages and attract more consumers.

\subparagraph{3. statement of the problem}
Akash DTH is offering 120 channels in their standard package. But there are lack of some popular channels.
\subparagraph{Details of Findings}
There are many types of taste of people. There are some popular channels which are missing. Which reduces customer satisfaction. Company is promised to give their level best try. They are adding popular channels consequently regarding user expectations.
\subparagraph{Recommendations and Conclusions}
As they were added popular channels previously based on user demand; They should add another some popular channels and make customers happy.

\subparagraph{4. statement of the problem}
The remote of the set top box is unique for one device. If the remote is damaged or lost user have to buy whole set top box which is costly and bothering.
\subparagraph{Details of Findings}
As we know, to consume DTH service a set top box is needed in consumers home; the set top box contains a remote to control the channels. Remote is frequently used and easy to damaged. But the remote is unique for one device. Consumer have to buy whole set top box if they lost of damaged their remote. It is as costly as bothering to user end.
\subparagraph{Recommendations and Conclusions}
We recommend company should provide multiple remote for one set top box. This can solve user bothering if they damage or lost their remote.

\subparagraph{5. statement of the problem}
Local political individuals or powerful people in cable operator business sometimes makes it difficult to provide DTH connection in particular areas.
\subparagraph{Details of Findings}
Sometimes in some particular areas it is not possible to provide connection even if the user wants it.There are a lot of providers of cable tv or dish tv connections.They try to use their power to stop providing DTH connection.
\subparagraph{Recommendations and Conclusions}
Companies are not always aware of this matter or they fail to take proper actions in every areas.They should take reports of every possible area and try to solve these problems.Thus they can grow a large number of users nationwide.


\subparagraph{6. statement of the problem}
They don’t have the feature of paying only for the channel we watch.
\subparagraph{Details of Findings}
 AKASH DTH packages are fixed priced with a fixed number of channels.But many people can’t afford that or they don’t want to see some channels yet they have to pay for it as it is in a package.
\subparagraph{Recommendations and Conclusions}
 AKASH DTH should make the feature pay for only the channels you watch available for their user.Thus a lot of people, even lower class people can afford DTH connection and the number of users will grow in a large number.



\subparagraph{7. statement of the problem}
Customer support is not available instantly,sometimes it takes longer in customer service and there is sometimes issue with the helpline.
\subparagraph{Details of Findings}
sometimes when people face issues with their set top box or connectivity they don’t get instant solution because of shortage of manpower in small cities or sometimes technical issues become hindrance to customer support.When people try to contact helpline they have to wait a longer time or if they faces problem in night they have to wait till next day.So the delayed customer service frustrates users.
\subparagraph{Recommendations and Conclusions}
We recommend companies should have a 24/7 helpline so that users can contact them whenever they face problem.The company should also increase manpower and should respond faster to ensure user satisfaction.
 
\subparagraph{PORTER’S Five Forces Analysis}
\subparagraph{Threat of new entry}
Currently there are not many reliable DTH providers in Bangladesh as AKASH DTH.So this is their chance to rule.

\subparagraph{Supplier power}
AKASH DTH has the ability and power to provide high quality product and service to the user.
\subparagraph{Buyer power}
Nowadays people are highly motivated to take satellite connection over cable connection .So they are willing to spend enough money in search of quality DTH tv connection.
\subparagraph{Threat of substitutiony}
As AKASH DTH is the only popular and reliable DTH provider in Bangladesh and they are emerging everyday the threat of substitution is very less.But this sector is going to get very saturated in future.

\section{Conclusion}
In the previous chapter, we discussed various problems and limitations of the existing systems. In this chapter, we further analyzed those problems and if any feasible solution exists or not, if any possible solution for a particular problem is worthy to implement or not.DTH is a new concept for people of Bangladesh.Many people do not have any idea about it.But yet a lot of people want good quality picture,variation of channels.AKASH DTH is trying their best to ensure customer satisfaction and needs.They can grow at large if they solve their problems and lackings. As Akash DTH is a profitable company we have considered their net growth and implantation costs before and after changing their existing policy. After initial study we find many potential in their business and marketing policies.  
\end{spacing}